\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[babel,english=british]{csquotes} % cool quotes
\usepackage[backend=biber,style=authoryear]{biblatex} % bibliogrpahy
\usepackage[utf8]{inputenc}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
%\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\usepackage[pagebackref=false,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%\let\cite\parencite
\addbibresource{literature.bib}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{Using Reinforcement Learning to play Connect Four}

\author{Raphael Michel
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Lucas-Raphael Müller
\and
Florian Störtz
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   Tbd.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

In this project, we try to use methods from Reinforcement Learning to solve
the well-known game \emph{Connect Four}, in which two players take turns in
inserting coins from the top into the columns of a $7\times 6$ grid board.
The first player who is able to establish four of their coins consecutively
within a column, row, or diagonal, wins the game.

It has been shown by Edelkamp and Kissmann that there are exactly $4\,531\,985\,219\,092$ legal positions in this game \cite{Edelkamp2008}. In the 1980s, two authors independently found a strategy for perfect playing of the game \cite{Allis88}\cite{Allen1990} that is quite complicated to perform. The game has since also been solved by brute force and and strong solvers have been created using minimax or negamax methods.

Our interest in this project is whether Reinforcement Learning methods will allow us to solve the game with less effort -- either less computational effort or less effort in algorithm design and implementation.

Additionally, we implement a traditional vision algorithm with the aim to
recognize the current game state of a Connect Four board from a photo of the
board. This could be seen as a proof of concept of creating an end-user friendly smartphone application that assists in playing the game.

\section{Methods}

\subsection{Prior Art}

\subsection{Vision}
We provide a framework which features extraction of game information(i.e. board configuration) by processing image data.
The board undergoes a variety of image processing steps and is then identified and checked.
In case the former process failed, the user is asked to retake the photograph.

\subsubsection{Object Detection using Haar-Like Features}
The very first step is detection of the connect4 board by using a Haar-Like feature incorporating Haar wavelet functions.
This processing step is done within the openCV framework \parencite{openCV}.
After the feature has been trained, the framework features the output of a \textit{Haar cascade xml-file} for fast object detection.

\paragraph{Training} has been performed on a set of 25 \textit{distinct} pictures wich were taken by hand (20) and from the internet (5).
Training of a Haar cascade needs many (in the order of thousands positive and negative samples;  \cite{kuranov}).




 by color and pattern comparision.
The image is then cropped and undergoes various image processing steps, such as wrapping, contrast enhancement and color channel extraction.
The current board configuration can then be read and converted to a computer readable format by thresholded color comparision.

\subsection{Game representation}
TBD
\subsection{Learning}
TBD


%-------------------------------------------------------------------------
\section{Results}

\subsection{Vision}
Processing time is $< 0.3$ s (i7-4790K CPU @ 4.00GHz) per image.


%-------------------------------------------------------------------------
\section{Discussion}

{\small
\printbibliography
}

\end{document}
